Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-18 presub/natastron_presub_coverletter.tex
remove principal authors
cover letter wording

\noindent I would like to express my interest in submitting a Letter to \emph{Nature Astronomy}, on the ``Detection of Oscillations in Aldebaran with Ground-Based Observations''. The principal authors are myself, Prof. Guy Davies (Birmingham), and Dr Benjamin Pope (NYU).

Aldebaran ($\alpha$~Tauri, the Eye of the Bull) is a nearby naked-eye red giant star. Since the identification of the planet candidate Aldebaran~b in~1993 in the first modern radial velocity (RV) surveys, a further two decades of observations have firmly established the existence of a massive planet around the star.

With radical new data processing techniques, we have re-analysed these historical RV data and augmented them with new observations of our own. Using our Gaussian Process-based model we infer much more accurate orbital parameters for the planet, but also detect the signal of stellar oscillations, missed by previous authors but uncovered by our powerful new algorithms. With asteroseismology we constrain the star's age for the first time, measure its mass with a factor of two better precision than had previously been possible (to 6\%), and consequently obtain the mass of the giant planet to a precision of 12\%.

We have also independently confirmed our results with new photometry from the \emph{Kepler}-2 (K2) mission, again using a highly novel data processing technique to extract a precise light curve of the brightest ever observed by \emph{Kepler}, ten thousand times above its saturation limit. The K2 light curve shows extremely clear oscillations that are in perfect agreement with the frequency we infer from RV.

@@

\closing{Yours sincerely, \\
\vspace{1.75cm}
Will Farr}

>>>>

\noindent I would like to express my interest in submitting a Letter to \emph{Nature Astronomy}, on the ``Detection of Oscillations in Aldebaran with Ground-Based Observations''.

Aldebaran ($\alpha$~Tauri, the Eye of the Bull) is a nearby first-magnitude red giant star. Since the identification of the planet candidate Aldebaran~b in~1993 in the first modern radial velocity (RV) surveys, the existence of a massive planet orbiting the star has been firmly established with a further two decades of observations.

One astronomer's noise is another astronomer's data: we have found that the noise in these archival observations is actually the signal of stellar oscillations. With radical new data processing techniques, we have re-analysed historical RV data and confirmed our result with new observations. Using our Gaussian Process-based model we detect the signal of stellar oscillations, missed by previous authors but uncovered by our powerful new algorithms, and consequently infer much more accurate orbital parameters for the planet. With asteroseismology we constrain the star's age for the first time, measure its mass with a factor of two better precision than had previously been possible (to 6\%), and consequently obtain the mass of the giant planet to a precision of 12\%.

We have also independently confirmed our results with new photometry from the \emph{Kepler}-2 (K2) mission, again using a highly novel data processing technique to extract a precise light curve of the brightest star ever observed by \emph{Kepler}. The K2 light curve shows extremely clear oscillations that are in perfect agreement with the frequency we infer from RV.

@@

\closing{Yours sincerely, \\
\vspace{1.5cm}
Will Farr}
